### 2021-07-28 paper/localpsf.tex
edits to impulse response regular grid discussion

Later we will need to perform function evaluations $z \mapsto \varphi_{x_i}(z)$ for a large number of points $z \in \Omega$. Using \eqref{eq:varphi_eval} to perform this task requires evaluating the function $\eta_b$ at a large number of points $z+x_i$. In computations the functions $\eta^b$ will be finite element functions formed on an irregular mesh, and the points $z+x_i$ will typically not be gridpoints of the mesh. Evaluating a finite element function at an arbitrary point requires finding which cell in the mesh that the point is in, and then evaluating several polynomial functions to evaluate the finite element function at the point in that cell. While this procedure is asymptotically scalable, it tends to be slow in practice \cite{FEMEVALSLOW}. To speed up evaluation of the function $\varphi_{x_i}$, we interpolate $\varphi_{x_i}$ onto a regular rectilinear grid on a coordinate axis aligned box that just barely contains the ellipsoid $E_{x_i}$. The function $\varphi_{x_i}$ is transferred from the irregular mesh to the regular rectilinear grid by evaluating $\varphi_{x_i}$ at all gridpoints in the regular rectilinear grid using \eqref{eq:varphi_eval} and the slow finite element evaluation process described previously. Once $\varphi_{x_i}$ has been transferred to the regular rectilinear grid, further evaluations of $\varphi_{x_i}$ are performed extremely quickly using standard algorithms for regular rectilinear grid interpolation. To minimize the error associated with transferring the function $\varphi_{x_i}$ from the irregular mesh to the regular rectilinear grid, the density of the regular rectilinear grid should be denser than the local density of the finite element mesh. In our numerical results, the distance between neighboring points in the regular rectilinear grid is chosen to be half the minimum distance between any pair of finite element Lagrange nodes that are contained in the ellipsoid $E_{x_i}$. This procedure is illustrated in Figure FIG.

>>>>

Later we will need to perform function evaluations $z \mapsto \varphi_{x_i}(z)$ for a large number of points $z$. Using \eqref{eq:varphi_eval} to perform this task requires evaluating the function $\eta_b$ at a large number of points $z+x_i$. In computations the functions $\eta^b$ will be finite element functions formed on an irregular mesh, and the points $z+x_i$ will typically not be gridpoints of the mesh. Evaluating a finite element function at an arbitrary point requires finding which cell in the mesh that the point is in, and then evaluating several polynomial functions to evaluate the finite element function at the point in that cell. While this procedure is asymptotically scalable, it tends to be slow in practice \cite{FEMEVALSLOW}. To speed up evaluation of the function $\varphi_{x_i}$, we interpolate $\varphi_{x_i}$ onto a regular rectilinear grid on a coordinate axis aligned box that just barely contains the ellipsoid $E_{x_i}$. The function $\varphi_{x_i}$ is transferred from the irregular mesh to the regular rectilinear grid by evaluating $\varphi_{x_i}$ at all gridpoints in the regular rectilinear grid using \eqref{eq:varphi_eval} and the slow finite element evaluation process described previously. Once $\varphi_{x_i}$ has been transferred to the regular rectilinear grid, further evaluations of $\varphi_{x_i}$ are performed using fast regular rectilinear grid interpolation. To limit the error associated with transferring the function $\varphi_{x_i}$ from the irregular mesh to the regular rectilinear grid, the density of the regular rectilinear grid should be denser than the local density of the finite element mesh. In our numerical results, the distance between neighboring points in the regular rectilinear grid is chosen to be half the minimum distance between any pair of finite element Lagrange nodes that are contained in the ellipsoid $E_{x_i}$. This grid transfer procedure is illustrated in Figure FIG.
